---
title: "Exam BIO302"
author: "Adam Haugen Mortensen"
format: html
editor: visual
---

## Part A - reproducibility

This text and code is archived at: [GitHub - adammo2904/exam23project](https://github.com/adammo2904/exam23project), and saved as "exambio302.qmd", the data for this part is found in the folder "reprod_data".

## Original paper and data source

I have chosen to look at this paper:

\- Knutsen, H., Jorde, P.E., Hutchings, J.A., Hemmer‐Hansen, J., Grønkjær, P., Jørgensen, K.E.M., André, C., Sodeland, M., Albretsen, J. and Olsen, E.M., 2018. Stable coexistence of genetically divergent Atlantic cod ecotypes at multiple spatial scales. *Evolutionary Applications*, *11*(9), pp.1527-1539.

And the data is available from the Dryad Digital Repository: [**https://doi.org/10.5061/dryad.hm249b5**](https://doi.org/10.5061/dryad.hm249b5).

## Continuing the attempt

Firstly loading the needed packages, as well as setting up Git and GitHub for the assignment.

```{r}
# Loading packages and setting up git
#| warning: false
library(here)
library(tidyverse)
library(dplyr)
library(usethis) #package for using git
here::here()
usethis::use_git()
use_github() #creating repository
```

loading the data.

```{r}
data <- read_delim(here("reprod_data", "data.csv")) |>
  janitor::clean_names() |>  #non capital column names
  count(year,origin) |> #Countinh the observations per year, for both origins
filter(origin != 0) |> #filter out data where the location is unknown
  drop_na(year)
```

As there is no label or readme for the data, i needed to figure out which one of the two origins is North Sea, and which one is Fjord. I choose to add a count into the data, which counts the number of observations for each origin for each year. For the year 2000, this showed 634 observations for origin 1, and 178 for origin 2. Comparing with the figure presented in the paper, Figure 2, tells me that origin 1 is probably Fjord, and 2 is North Sea. This is because the figure presents a much higher number of observations for Fjord. Though there is a discrepancy between the actual numbers i found in the data, and those in the paper, which i will come back to later.

Plotting the data in the same manner as presented in the paper:

```{r}
plot1 <- ggplot(data = data, aes(x = year, y = n, colour = factor(origin))) +
  geom_line() +
  theme_bw()

plot1
```

2.  Discuss how well you managed to reproduce the part of paper you were working on and what challenges you faced. If you looked at two papers discuss both.

3.  Discuss what how well the original paper meets best practice for reproducibility, i.e. what should the authors have done to make their analysis more reproducible, and what they did well.
