---
title: "Exam BIO302"
author: "Adam Haugen Mortensen"
format: html
editor: visual
---

## Part A - reproducibility

## Original paper and data source

I have chosen to look at this paper:

\- Knutsen, H., Jorde, P.E., Hutchings, J.A., Hemmer‐Hansen, J., Grønkjær, P., Jørgensen, K.E.M., André, C., Sodeland, M., Albretsen, J. and Olsen, E.M., 2018. Stable coexistence of genetically divergent Atlantic cod ecotypes at multiple spatial scales. *Evolutionary Applications*, *11*(9), pp.1527-1539.

And the data is available from the Dryad Digital Repository: [**https://doi.org/10.5061/dryad.hm249b5**](https://doi.org/10.5061/dryad.hm249b5).

1.  Continue with your attempt to reproduce part of a paper from archived data from the first practical. Archive the code and text on GitHub and include the link to your repo in your answer here.

-   Make at least two commits to git.
-   Make your reproduction as reproducible as possible (i.e. it should be possible for me to reproduce your work after cloning your repo and downloading the data).

```{r}
# Loading packages and setting up git
#| warning: false
library(here)
library(tidyverse)
library(dplyr)
library(usethis) #package for using git
here::here()
usethis::use_git()
use_github() #creating repository
```

2.  Discuss how well you managed to reproduce the part of paper you were working on and what challenges you faced. If you looked at two papers discuss both.

3.  Discuss what how well the original paper meets best practice for reproducibility, i.e. what should the authors have done to make their analysis more reproducible, and what they did well.

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
